You can find the Repository here: https://github.com/darthkali/WeeFood

All test are shared between \ios and Android. In the \inlineCode{.run} directory are 2 configurations. These
configurations run all Test (separate for \ios and Android) at once.

\textbf{Run \ios App}\newline
To run the \ios app you need to follow these Steps:

\begin{enumerate}
    \item rebuild the app in Android Studio [Taskbar in AS -> Build -> Rebuild Project]
    \item After that you need Xcode. In the App Folder is a \inlineCode{iosWeeFood} Folder. From there you can open the workspace-file in xcode.
\end{enumerate}


\textbf{Issues when building the \ios app}\newline
In Case you never run a app in XCode there might be some issues. For some of them i have found a solution. At first: Some Solutions must run twice. And sometimes you need to rebuild the app in Android Studio again.

\textbf{No Gradle Permission}
\begin{enumerate}
    \item open the Terminal in root directory from the app
    \item run: \inlineCode{chmod +x gradlew} to give full permission
\end{enumerate}


\textbf{gradlew wrapper is missing}
\begin{enumerate}
    \item open the Terminal in root directory from the app
    \item run: \inlineCode{gradle; gradle wrapper}
\end{enumerate}
if gradle is missing: install gradle via terminal run: \inlineCode{brew install gradle}

\textbf{shared or other modules are missing}
\begin{enumerate}
     \item open the Terminal in \inlineCode{iosWeeFood} directory from the app
     \item run: \inlineCode{pod deintegrate; pod install} to clean the pod and reinstall it
\end{enumerate}


\textbf{SQL-Delight problems}
\begin{enumerate}
    \item go in xcode to the root project
    \item Build Settings -> Linking -> Other Linker Flag
    \item Set a new variable \inlineCode{-lsqlite3}
\end{enumerate}


\textbf{no command line tool set}
\begin{enumerate}
    \item go in xcode to settings -> locations
    \item set a xcode version in the command line tool sections
\end{enumerate}


